Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-08-26 Manuscript/manuscript.Rmd
edits

![**Models built using distance-type functional genomic annotations combined with SMOTE re-sampling yielded optimal MCCs across resolution.** Barplots comparing the performances of random forest classifiers built using different combinations of data level characteristics. Within each re-sampling technique (A-D), performances are compared for each type of feature space: OC (red), OP (green), and Distance (blue), across resolutions. Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/model_performances_v3_bars.png)

@@

![**Assessing top ranked transcription factors in TAD boundary prediction.** (A) (B) (C)](Figures/annot_specific_rfe_varimps_heatmap.png)

## Top TFBS were more enriched at predicted TAD boundaries at bp resolution than those provided by the TAD caller kb resolution

>>>>

![**Models built using distance-type predictors combined with SMOTE re-sampling yielded optimal MCCs across resolution.** Barplots comparing the performances of random forest classifiers built using different combinations of data level characteristics. Within each re-sampling technique (A-D), performances are compared for each type of feature space: OC (red), OP (green), and Distance (blue), across resolutions. Performances were evaluated using MCCs and aggregated by averaging across each chromosome, with error bars representing 1 standard deviation away from the mean.](Figures/model_performances_v3_bars.png)

@@

![**Assessing top ranked transcription factors in TAD boundary prediction.** (A) Barplots comparing performances of models using specific groups of functional genomic annotation as the feature space including histone modifications (HM; red), chromatin states (ChromHMM; green), transcription factor binding sites (TFBS; blue), in addition to a model with a feature space containing all 3 groups (Combined; purple). Error bars represent $\pm$ 1 standard deviation from the mean MCC across each chromosomal section of the linear genome. (B) Recursive feature elimimation analysis used to reduce the number of TFBS to include in the optimally build random forest classifier. Error bars represent 1 standard deviation away from the mean cross-validated MCC. (C) Clustered heatmap of variable importances for the union of the top 8 most predictive TFBS across chromosomes.](Figures/annot_specific_rfe_varimps_heatmap.png)

## LEVERAGING ChIP-seq PEAK REGIONS OF TOP PREDICTIVE TFBS PROVIDE MORE PRECISE LOCATION OF TAD BOUNDARIES
